---
title: "Getting Started with dieroll"
author: "Qinyi Yang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to cointoss}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(dieroller)
```

#die roll
```{r}
#The package "dieroll" is a minimal implementation for simulating tossing a die a given number of times, and to visualize the relative frequencies in such a series of rolls.
```

## die rollinng

The package `"dieroller"` is a minimal implementation for simulating rolling a die a given number of times, and to visualize the relative frequencies in such a series of roll.


## Creating a `die`

The first step is to create a `"die"` object with the function `die()`:

```{r}
fair_die <- die() 
fair_die
```

By default, `die()` creates a _fair_ die 

You can change the defatuls with arguments `sides` and `prob`:

```{r}
loaded_die <- die(prob = c(0.075, 0.1, 0.125, 0.15, 0.20, 0.35))
loaded_die
```


## rolling a die

Once you have defined a `"die"` object, you can use the function `roll()` to
_roll_ a coin a given number of `times`. The output will be an object of class `"rool"`, which will contain the vector of `roll`:

```{r}
set.seed(123)
fair_50rolls <- roll(fair_die, times = 50)
fair_50rolls
```

The `summary()` function gives you a nice table of frequencies:
```{r}
set.seed(123)
fair_50rolls <- roll(fair_die, times = 50) 
fair50_sum <- summary(fair_50rolls)
fair50_sum
```


## Plot of relative frequencies

You can use the function `plot()` to create a graohic with the relative 
frequencies of a series of die roll:

```{r, fig.show='hold'}
plot(fair_50rolls)
```



